The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-05 src/ms.tex
Fix a comma splice
I split it into two sentences, but a semicolon or mdash would also work.

% Much of this text was adapted from Robel Geda's report from NSBP and
% SACNAS. Please include him on the author list.
\textbf{\astropy representation at national diversity conferences:}
Several members of the \astropy community attended virtual conferences of the
National Society of Black Physicists (NSBP) and SACNAS (focusing on Hispanic and
Native American scientists across all STEM fields). \astropy representatives
noted that one underlying topic came up multiple times. A major barrier for
persons who come from underrepresented communities is the lack of resources and
expertise that are necessary to train students. Writing PEP 8-compliant software
and understanding the Git and \github workflow is not part of the standard
Physics and Astrophysics curriculum. Additionally, the larger astronomical
community is still in the process of transitioning towards \python-based tools,
making it difficult for students not currently under advisement by some one with
extensive \python expertise to get involved with the open source \python
community. Projects such as Learn Astropy (see Section~\ref{sec:learn}) could
have a profound impact by empowering underrepresented groups because it provides
a free, searchable, and accessible introduction to \python tools for
astrophysical research. Representatives also noted that offering training and
teaching materials to PIs of Research Experience for Undergraduate (REU)
programs throughout the United States could be helpful for encouraging advisors
to teach students how to use Astropy, create their own libraries, and use
version control on open source platforms like \github. Such materials could also
be offered as a workshop at national diversity conferences themselves, as SACNAS
solicits special session proposals each year.

@@

The Cherenkov Telescope (CTA) will be the next generation very-high-energy
gamma-ray observatory.
CTA will improve over the current generation of imaging atmospheric Cherenkov telescopes (IACTs)
by a factor of five to ten in sensitivity and will be able to observe the whole sky from a combination of two sites:
a northern site in La Palma, Spain, and a southern one in Paranal, Chile.
CTA will be able to observe gamma rays in a broad energy range from around $20\,\mathrm{GeV}$ to over $300\,\mathrm{TeV}$
using three different types of telescopes, in total over 100 telescopes are planned at the two sites.
CTA will also be the first open gamma-ray observatory.

>>>>

% Much of this text was adapted from Robel Geda's report from NSBP and
% SACNAS. Please include him on the author list.
\textbf{\astropy representation at national diversity conferences:}
Several members of the \astropy community attended virtual conferences of the
National Society of Black Physicists (NSBP) and SACNAS (focusing on Hispanic and
Native American scientists across all STEM fields). \astropy representatives
noted that one underlying topic came up multiple times. A major barrier for
persons who come from underrepresented communities is the lack of resources and
expertise that are necessary to train students. Writing PEP 8 compliant software
and understanding the Git and \github workflow is not part of the standard
Physics and Astrophysics curriculum. Additionally, the larger astronomical
community is still in the process of transitioning towards \python-based tools,
making it difficult for students not currently under advisement by some one with
extensive \python expertise to get involved with the open source \python
community. Projects such as Learn Astropy (see Section~\ref{sec:learn}) could
have a profound impact by empowering underrepresented groups because it provides
a free, searchable, and accessible introduction to \python tools for
astrophysical research. Representatives also noted that offering training and
teaching materials to PIs of Research Experience for Undergraduate (REU)
programs throughout the United States could be helpful for encouraging advisors
to teach students how to use Astropy, create their own libraries, and use
version control on open source platforms like \github. Such materials could also
be offered as a workshop at national diversity conferences themselves, as SACNAS
solicits special session proposals each year.

@@

The Cherenkov Telescope (CTA) will be the next generation very-high-energy
gamma-ray observatory.
CTA will improve over the current generation of imaging atmospheric Cherenkov telescopes (IACTs)
by a factor of five to ten in sensitivity and will be able to observe the whole sky from a combination of two sites:
a northern site in La Palma, Spain, and a southern one in Paranal, Chile.
CTA will be able to observe gamma rays in a broad energy range from around $20\,\mathrm{GeV}$ to over $300\,\mathrm{TeV}$
using three different types of telescopes. In total over 100 telescopes are planned at the two sites.
CTA will also be the first open gamma-ray observatory.
